---
title: "Graph_New"
author: "Luisa Jansen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Load Packages

```{r Pakete, message = FALSE}
library(remotes)
library(rlang)
library(ggpattern)
library(dplyr)
library(ggplot2)
library(readxl)
library(data.table)
library(tibble)
library(tidyr)
library(stringr)
library(wesanderson)
```

#### Load Data

```{r}
wholedata <- read_csv2("../results/Single Study.csv")

data_cause <- wholedata[, c("cause_variables_new", "cause_variables_theory", "cause_variables_theory_other")]
data_cause <- rowid_to_column(data_cause, "ID")

data_outcome <- wholedata[ , c("outcome_variables_new", "outcome_variables_theory")]
data_outcome <- rowid_to_column(data_outcome, "ID")

```

#### Create Dataframe for Cause Variables

```{r}
# Split "cause_variables_theory_other" and "cause_variables_theory". 
max(lengths(strsplit(as.character(data_cause$cause_variables_theory_other), '; '))) # 8
setDT(data_cause)[, paste0("cause_variables_theory_other", 1:8) := tstrsplit(data_cause$cause_variables_theory_other, "; ")]

max(lengths(strsplit(as.character(data_cause$cause_variables_theory), '; '))) # 9
data_cause <- setDT(data_cause)[, paste0("cause_variables_theory", 1:9) := tstrsplit(data_cause$cause_variables_theory, "; ")]

# Loop over all rows and "cause_variables_theory" columns to replace "other" values.
for (i in 1:186) {
  k <- 0;
  for(j in 13:21) { 
   l <- k + 5; 
   if(grepl("other", data_cause[i, ..j]) == TRUE) {
      data_cause[i,j] <- data_cause[i, ..l]; k <- k + 1}}}

# create new column with groups 
data_cause <- unite(data_cause, col='cause_variables_groups', c('cause_variables_theory1', 'cause_variables_theory2', 'cause_variables_theory3', 'cause_variables_theory4', 'cause_variables_theory5', 'cause_variables_theory6', 'cause_variables_theory7', 'cause_variables_theory8', 'cause_variables_theory9'), sep=';', na.rm = TRUE)

# create new dataframe with only relevant columns
data_cause_short <- data_cause[, c("cause_variables_new", "cause_variables_groups")]

# convert into long format
data_cause_short <- separate_rows(data_cause_short, cause_variables_new, cause_variables_groups, sep = ";")

# delete whitespaces at beginning of rows
data_cause_short <- data_cause_short %>% mutate(cause_variables_new = trimws(cause_variables_new))

# Delete empty rows
data_cause_short <- data_cause_short[complete.cases(data_cause_short), ]

# Sort alphabetically
data_cause_short <- data_cause_short[order(data_cause_short$cause_variables_new),]

# Save data
write.csv2(data_cause_short, "../../data/processed/ListOfCauseVariables.csv")

```


#### Create Dataframe for Outcome Variables

```{r}
# convert to long format
data_outcome <- separate_rows(data_outcome, outcome_variables_new, outcome_variables_theory, sep = ";")

data_outcome <- data_outcome[-c(1)]

# delete whitespaces at beginning of rows
data_outcome <- data_outcome %>% mutate(outcome_variables_new = trimws(outcome_variables_new))

data_outcome <- data_outcome %>% mutate(outcome_variables_theory = trimws(outcome_variables_theory))

# Delete empty rows
data_outcome <- data_outcome[complete.cases(data_outcome), ]

# Sort alphabetically
data_outcome <- data_outcome[order(data_outcome$outcome_variables_new),]

# Save dataframe
write.csv2(data_outcome, "../../data/processed/ListOfOutcomeVariables.csv")
```


### Create Graph

## Preparation 

Read Dataframes with Cause Variables and their groups as well as Outcome Variables and their groups
```{r}
data_outcome <- read.csv2("../../data/processed/ListOfOutcomeVariables.csv")

data_cause <- read.csv2("../../data/processed/ListOfCauseVariables.csv")

# Delete ID columns
data_outcome <- subset(data_outcome, select = -X)
data_cause <- subset(data_cause, select = -X)

# Rename column headers
data_outcome <- data_outcome %>% 
  rename(Group = outcome_variables_theory,
         Construct = outcome_variables_new)
data_cause <- data_cause %>% 
  rename(Group = cause_variables_groups,
         Construct = cause_variables_new)

# Separate Cause Variables with multiple groups (each variable can now have multiple groups) 
data_cause_multiple <- 
  separate_rows(data_cause, Group, sep = ",")
data_cause_multiple$Group <- 
  gsub(" ", "", data_cause_multiple$Group)

# Sum up "other" category
data_cause_multiple$GroupNew <-
  ifelse(data_cause_multiple$Group == "cognitive" |
           data_cause_multiple$Group == "demographics",
         "other", 
         data_cause_multiple$Group)
```

Create dataframes with variables that are both outcome as well as cause variables
```{r}
data_both <- na.omit(left_join
                     (data_outcome, data_cause_multiple, 
                       by = "Construct"))

# Create List with "both variables" 
ListOfBothConstructs <- 
  data.frame(data_both$Construct) %>% distinct()

# Convert to String
BothVariables <-
  c(toString(ListOfBothConstructs$data_both.Construct))
BothVariables

# Align List (copied in with " " around each word) with "outcome variables"
data_outcome_both <- data_outcome[data_outcome$Construct %in% c("attitude", "avoidance behavior", "awareness", "competition effectiveness for recruitment", "competition performance and satisfaction", "concerns", "effort", "expertise", "hearsay", "interest", "job satisfaction", "literacy", "organizational fit", "perceived risk", "problematic behavior", "protection behavior", "response efficacy", "sharing", "system satisfaction"),]

# Align List (coped in with " " around each word) with "cause variables"
data_cause_both <- data_cause_multiple[data_cause_multiple$Construct %in% c("attitude", "avoidance behavior", "awareness", "competition effectiveness for recruitment", "competition performance and satisfaction", "concerns", "effort", "expertise", "hearsay", "interest", "job satisfaction", "literacy", "organizational fit", "perceived risk", "problematic behavior", "protection behavior", "response efficacy", "sharing", "system satisfaction"),]
```

Calculate frequency of constructs in each group
```{r}
# Outcome Groups
table(data_outcome$Group)
outcome_frequency <- 
  as.data.frame(table(data_outcome$Group))
outcome_frequency <- 
  outcome_frequency %>% rename(group = Var1, frequency = Freq)
outcome_frequency

# Cause Groups (each variable can have multiple groups)
table(data_cause_multiple$GroupNew)
cause_frequency <-
  as.data.frame(table(data_cause_multiple$GroupNew))
cause_frequency <- 
  cause_frequency %>% rename(group = Var1, frequency = Freq)
cause_frequency

# Outcome in Both
table(data_outcome_both$Group)
outcome_both_frequency <-
  as.data.frame(table(data_outcome_both$Group))
outcome_both_frequency <- 
  outcome_both_frequency %>% 
  rename(group = Var1, frequency = Freq)
outcome_both_frequency

# Cause in Both (each variable can have multiple groups)
table(data_cause_both$GroupNew)
cause_both_frequency <- 
  as.data.frame(table(data_cause_both$GroupNew))
cause_both_frequency <- 
  cause_both_frequency %>% 
  rename(group = Var1, frequency = Freq)
cause_both_frequency
```


## Create Graphs

### Outcome Variables 

```{r}
wes_color <- 
  wes_palette("FantasticFox1", 4, type = c("discrete"))[3:4]

barplot_outcome <- 
  ggplot(data = outcome_frequency, aes(x = group, y = frequency))+
  geom_bar(stat = "identity", fill = wes_color[1]) +
  coord_flip() +
  theme_void() +
  ggtitle("Outcome Variables \n") +
  ylim(0,100) +
  theme(plot.title = element_text(hjust = 0.5, family = "serif", size = 30)) +
  scale_x_discrete(limits = c("other", "control", "motivation", "intention", "behavior"))+
  # geom_text(aes(label = frequency), vjust = 0.3, size = 4, nudge_y = -2.5, col = "white", family = "serif")+ 
  geom_text(aes(label = c("Behavior", "Control", "Intention", "Motivation", "Other")),family = "serif", 
            vjust = 0.3, size = 5, nudge_y = c(10,9,10,12,6), col = "black")

ggsave("../results/outcome.png", bg = "white")

barplot_outcome
```

### Cause Variables

```{r, message = FALSE}
barplot_cause <- ggplot(data = cause_frequency, aes(x = group, y = frequency))+
  geom_bar(stat = "identity", fill = wes_color[2], width = 0.9) +
  coord_flip() +
  theme_void() +
  ggtitle("Cause Variables \n") +
  theme(plot.title = element_text(hjust = 0.5, family = "serif", size = 30)) +
  scale_x_discrete(limits = c("other", "vicariousexperience", "emotionalarousal", "persuasion", "mastery"))+
  # geom_text(aes(label = frequency), vjust = 0.3, size = 4, nudge_y = 2.5, col = "white", family = "serif")+ 
  geom_text(aes(label = c("Emotional Arousal", "Mastery", "Other", "Persuasion", "Vicarious Experience")),family = "serif", vjust = 0.3, size = 5, nudge_y = c(-18,-12,-10,-12,-19), col = "black")+
  scale_y_reverse(limits=c(100,0)) 


ggsave("../results/cause.png", bg = "white")

barplot_cause
```

### Both Variables
#### Outcome Both
```{r}
barplot_outcome_both <- ggplot(data = outcome_both_frequency, aes(x = group, y = frequency))+
  geom_bar(stat = "identity", fill = wes_color[1], width = 0.9) +
  geom_col_pattern(fill = wes_color[1], colour = "white",
                   pattern='stripe', pattern_size = 0.1, pattern_spacing = 0.07) +
  coord_flip() +
  theme_void() +
  ggtitle("Both Variables in Outcome Groups\n") +
  ylim(0,100) +
  theme(plot.title = element_text(hjust = 0.5, family = "serif", size = 30)) +
  scale_x_discrete(limits = c("other", "behavior"))+
  #geom_text(aes(label = frequency), vjust = 0.3, size = 4, nudge_y = -2.5, col = "white", family = "serif")+ 
  geom_text(aes(label = c("Behavior", "Other")),family = "serif", vjust = 0.3, size = 5, nudge_y = c(9,10), col = "black")

ggsave("../results/outcome_both.png", bg = "white")

barplot_outcome_both
```
#### Cause Both
```{r, message = FALSE}
barplot_cause_both <- ggplot(data = cause_both_frequency, aes(x = group, y = frequency))+
  geom_bar(stat = "identity", fill = wes_color[2], width = 0.9) +
  geom_col_pattern(fill = wes_color[2], colour = "white",
                   pattern='stripe', pattern_size = .1, pattern_spacing = 0.07) +
  coord_flip() +
  theme_void() +
  ggtitle("Both Variables in Cause Groups \n") +
  theme(plot.title = element_text(hjust = 0.5, family = "serif", size = 30)) +
  scale_x_discrete(limits = c("other", "vicariousexperience", "persuasion", "mastery"))+
  # geom_text(aes(label = frequency), vjust = 0.3, size = 4, nudge_y = 2.5, col = "white", family = "serif")+ 
  geom_text(aes(label = c("Mastery", "Other", "Persuasion", "Vicarious Experience")),family = "serif",  
            vjust = 0.3, size = 5, nudge_y = c(-16,-12,-10,-20), col = "black")+
  scale_y_reverse(limits=c(100,0)) 


ggsave("../results/cause_both.png", bg = "white")

barplot_cause_both
```


